---
title: "Experiment 5 (Spatial Overlap)"
author: "Hyuksu Lee, Do-Joon Yi"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapse: false
      smooth_scroll: false
    number_sections: true
    theme: cosmo 
    highlight: haddock
    code_folding: hide
subtitle: Effects of visual short-term memory load on response selection
mainfont: Noto Sans CJK KR
---

```{r wd, echo=FALSE}
setwd("~/Documents/GitHub/vstmAS/")
```

```{css, echo=FALSE}
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
```

```{r setup, message=FALSE}
set.seed(12345) # for reproducibility
options(knitr.kable.NA = '')

# Some packages need to be loaded. We use `pacman` as a package manager, which takes care of the other packages. 
if (!require("pacman", quietly = TRUE)) install.packages("pacman")
if (!require("Rmisc", quietly = TRUE)) install.packages("Rmisc") # Never load it directly.
pacman::p_load(tidyverse, knitr,
               powerAnalysis, afex, emmeans, BayesFactor, 
               ggstatsplot)
pacman::p_load_gh("thomasp85/patchwork", "RLesur/klippy")

klippy::klippy()
```

# Data

A short version of task description here.

```{r data, collapse=TRUE}
E5 <- read.csv("data/data_vstmAS5.csv", header = T)

E5$SN <- factor(E5$SN)
E5$vstmLoad <- factor(E5$vstmLoad, levels=c(1,2), labels=c("LowLoad","HighLoad"))
E5$Congruency <- factor(E5$Congruency, levels=c(0,1), labels=c("Incongruent","Congruent"))
E5$Overlap <- factor(E5$Overlap, levels=c(0,1), labels=c("NonOverlap","Overlap"))
E5$Corr <- ifelse(E5$Targ==E5$Resp,1,0)
E5$vstmCorr <- ifelse(E5$vstmCond==E5$vstmResp,1,0)

# Description of raw data columns.
# 1. SN: participant ID
# 2. Trial: 1~384
# 3. Block: 1~8
# 4. vstmLoad: VSTM load. 1 = low, 2 = high
# 5. Overlap: 0 = Non overlap, 1 = Overlap
# 6. Targ: target type. 1 or 2
# 7. Flnk: flanker type. 1 or 2
# 8. TargPos: target position. 1~6
# 9. FlnkPos: flanker position. 1 or 2
# 10. Congruency: 0 = incongruent, 1 = congruent
# 11. Resp: 1 or 2, 7 = no response
# 12. RT: response time in second
# 13. vstmPos: VSTM sample position. 1 or 2
# 14. vstmCond: change = 1 or not = 2
# 15. vstmResp: 1 or 2, 7 = no response
# 16. vstmRT: response time in second
# 17. Corr: attention task correctness, 1=correct, 0 = incorrect
# 18. vstmCorr: VSTM task correctness, 1=correct, 0 = incorrect

glimpse(E5, width=70)

```

**Spatial overlap**, **VSTM Load**, and **congruency** were within-subject factors.

```{r design}
table(E5$Overlap, E5$SN) %>% kable()
table(E5$vstmLoad, E5$SN) %>% kable()
table(E5$Congruency, E5$SN) %>% kable()
```


<br><br>

****

<br><br>


# Change Detection Task

## Accuracy

```{r vstm_sum}
# VSTM, Experiment 5, subject-level, long format
vE5slong <- E5 %>% group_by(SN, Overlap, vstmLoad) %>% 
  summarise(vstmCorr = mean(vstmCorr)*100) %>% 
  ungroup()

# Experiment 5 summary
vE5slong %>% group_by(Overlap, vstmLoad) %>% 
  summarise(M = mean(vstmCorr), SD = sd(vstmCorr)) %>% 
  ungroup() %>% 
  kable()

# wide format, needed for geom_segments.
vE5swide <- vE5slong %>% unite("temp", c("Overlap", "vstmLoad")) %>% 
  spread(key = temp, value = vstmCorr)

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
vE5g <- Rmisc::summarySEwithin(data = vE5slong, measurevar = "vstmCorr", 
                               withinvars = c("vstmLoad", "Overlap"), idvar = "SN")

p1 <- ggplot(filter(vE5slong, Overlap=="NonOverlap"), aes(x=vstmLoad, y=vstmCorr)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  geom_point(color="gray80", size=1.8) +
  geom_segment(data=vE5swide, aes(x=1, y=vE5swide$NonOverlap_LowLoad, xend=2, 
                   yend=vE5swide$NonOverlap_HighLoad), color="gray80") +
  geom_pointrange(filter(vE5g, Overlap=="NonOverlap"), inherit.aes=FALSE,
                  mapping=aes(x = vstmLoad, y=vstmCorr, 
                              ymin = vstmCorr - ci, ymax = vstmCorr + ci), 
                  colour="darkred", size = 1) +
  labs(title = "Non-Overlap", x = "VSTM Load", y = "Change Detection Accuracy") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5))

p2 <- ggplot(filter(vE5slong, Overlap=="Overlap"), aes(x=vstmLoad, y=vstmCorr)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  geom_point(color="gray80", size=1.8) +
  geom_segment(data=vE5swide, aes(x=1, y=vE5swide$Overlap_LowLoad, xend=2, 
                   yend=vE5swide$Overlap_HighLoad), color="gray80") +
  geom_pointrange(filter(vE5g, Overlap=="Overlap"), inherit.aes=FALSE,
                  mapping=aes(x = vstmLoad, y=vstmCorr, 
                              ymin = vstmCorr - ci, ymax = vstmCorr + ci), 
                  colour="darkred", size = 1) +
  labs(title = "Overlap", x = "VSTM Load", y = "Change Detection Accuracy") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

p1 + p2
```

### ANOVA


```{r vstm_aov, warning=FALSE, message=FALSE}
aov_ez(id = "SN", data = vE5slong, dv = "vstmCorr", within = c("vstmLoad","Overlap")) %>% 
  anova(es = "pes") %>% kable(digits = 4)
```

<br><br>

****

<br><br>



# Flanker Task

Accuracy in the attention task was generally high. There were no significant effects in the ANOVA. 

## Accuracy

```{r attention_acc}
aE5slong <- E5 %>% group_by(SN, vstmLoad, Overlap, Congruency) %>% 
  summarise(Accuracy = mean(Corr)*100, N = n()) %>% 
  ungroup()

aE5slong %>% group_by(Overlap, vstmLoad, Congruency) %>% 
  summarise(M = mean(Accuracy),
            SD = sd(Accuracy)) %>% 
  ungroup() %>% 
  kable()

aE5g <- Rmisc::summarySEwithin(data = aE5slong, measurevar = "Accuracy", 
                       withinvars = c("vstmLoad", "Overlap", "Congruency"), idvar = "SN") 

w1 <- ggplot(data=filter(aE5slong, Overlap=="NonOverlap"), aes(x=vstmLoad, y=Accuracy, fill=Congruency)) +
  geom_violin(width = 0.7, trim=TRUE) +
  ggbeeswarm::geom_quasirandom(dodge.width = 0.7, color = "gray80", size = 3, alpha = 0.4, 
                               show.legend = FALSE) +
  geom_pointrange(data=filter(aE5g, Overlap=="NonOverlap"),
                  aes(x = vstmLoad, ymin = Accuracy-ci, ymax = Accuracy+ci, color = Congruency),
                  position = position_dodge(0.7), color = "darkred", size = 1, show.legend = FALSE) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  labs(title = "Non-Overlap",
       x = "VSTM Load", 
       y = "Accuracy (%)", 
       fill="Congruency") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  theme_bw(base_size = 18) +
  theme(legend.position = "none", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5)) 

w2 <- ggplot(data=filter(aE5slong, Overlap=="Overlap"), aes(x=vstmLoad, y=Accuracy, fill=Congruency)) +
  geom_violin(width = 0.7, trim=TRUE) +
  ggbeeswarm::geom_quasirandom(dodge.width = 0.7, color = "gray80", size = 3, alpha = 0.4, 
                               show.legend = FALSE) +
  geom_pointrange(data=filter(aE5g, Overlap=="Overlap"),
                  aes(x = vstmLoad, ymin = Accuracy-ci, ymax = Accuracy+ci, color = Congruency),
                  position = position_dodge(0.7), color = "darkred", size = 1, show.legend = FALSE) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  labs(title = "Overlap",
       x = "VSTM Load", 
       y = "Accuracy (%)", 
       fill="Congruency") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = c(.6, .2)) 

w1 + w2
```

### ANOVA

```{r attention_aov, attention_aov, warning=FALSE, message=FALSE}
aov_ez(id = "SN", data = aE5slong, dv = "Accuracy", within = c("vstmLoad", "Overlap", "Congruency")) %>% 
  anova(es = "pes") %>% kable(digits = 4)
```

<br><br>

****

<br><br>


## RT

### Trimming

```{r trimming}
# filtering out incorrect trials
cE5 <- E5 %>% filter(Corr==1 & vstmCorr==1) %>% mutate(RT = RT*1000)

# trimming by 2.5 MAD.
rE5 <- cE5 %>% filter(RT > 200) %>% 
  group_by(SN) %>% 
  nest() %>% 
  mutate(lbound = map(data, ~median(.$RT)-2.5*mad(.$RT)),
         ubound = map(data, ~median(.$RT)+2.5*mad(.$RT))) %>% 
  unnest(lbound, ubound) %>% 
  unnest(data) %>% 
  mutate(Outlier = (RT < lbound)|(RT > ubound)) %>% 
  filter(Outlier == FALSE) %>% 
  ungroup %>%
  select(SN, Overlap, vstmLoad, Congruency, RT, vstmRT)

# percentage trimmed.
(nrow(cE5)-nrow(rE5))/nrow(cE5)
```

`r round(100*(nrow(cE5)-nrow(rE5))/nrow(cE5), digits=2)`%의 가외치가 제거되었다.

```{r rt_distribution, fig.asp = .4}
den1 <- ggplot(cE5, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den2 <- ggplot(rE5, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) + 
  labs(x = "Trimmed RT") + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den1 + den2
```


### Mean RTs

```{r 8con_rt_sum}
# Attention RT, Experiment 5, subject-level, long format
rE5slong <- rE5 %>% group_by(SN, Overlap, vstmLoad, Congruency) %>% 
  summarise(RT = mean(RT)) %>% 
  ungroup()

# Experiment 5 summary
rE5slong %>% group_by(Overlap, vstmLoad, Congruency) %>% 
  summarise(M = mean(RT), SD = sd(RT)) %>% 
  ungroup() %>% 
  kable()

# wide format, needed for geom_segments.
rE5swide <- rE5slong %>%  
  unite("temp", c("vstmLoad", "Congruency")) %>% 
  spread(key = temp, value = RT)

# group level, needed for printing & geom_pointrange
rE5g <- Rmisc::summarySEwithin(data = rE5slong, measurevar = "RT", 
                               withinvars = c("vstmLoad", "Overlap", "Congruency"), idvar = "SN") 

```

### RT Congruency Effect

```{r congruency_sum}
# Four conditions summary long format
rE5CEslong <- rE5slong %>%
  spread(key = Congruency, value = RT) %>% 
  mutate(cEffect = Incongruent - Congruent) %>% 
  select(SN, Overlap, vstmLoad, cEffect)

rE5CEslong %>% group_by(Overlap, vstmLoad) %>% 
  summarise(M = mean(cEffect), SD = sd(cEffect)) %>% 
  ungroup() %>% 
  kable()

rE5CEswide <- rE5CEslong %>% 
  unite("temp", c("Overlap", "vstmLoad")) %>% 
  spread(key = temp, value = cEffect)

rE5CEg <- Rmisc::summarySEwithin(data = rE5CEslong, measurevar = "cEffect", 
                               withinvars = c("Overlap", "vstmLoad"), idvar = "SN") 
```

```{r rt_plots, fig.height=10}
# Eight conditions
r1 <- ggplot() + 
  geom_bar(data=filter(rE5g, Overlap=="NonOverlap"), aes(x=vstmLoad, y=RT, fill=Congruency),
           stat="identity", width=0.7, color="black", position=position_dodge(.8)) + 
  geom_linerange(data=filter(rE5g, Overlap=="NonOverlap"), 
                 aes(x=vstmLoad, ymin=RT-ci, ymax=RT+ci, group=Congruency),
                 size=1, position=position_dodge(0.8)) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  geom_point(data=filter(rE5slong, Overlap=="NonOverlap"), 
             aes(x=vstmLoad, y=RT, group=Congruency),
             position=position_dodge(0.6), color="gray80", size=1.8) +
  geom_segment(data=filter(rE5swide, Overlap=="NonOverlap"), 
               aes(x=1-.15, y=filter(rE5swide, Overlap=="NonOverlap")$LowLoad_Incongruent,
                   xend=1+.15, yend=filter(rE5swide, Overlap=="NonOverlap")$LowLoad_Congruent),
               color="gray80") +
  geom_segment(data=filter(rE5swide, Overlap=="NonOverlap"), 
               aes(x=2-.15, y=filter(rE5swide, Overlap=="NonOverlap")$HighLoad_Incongruent,
                   xend=2+.15, yend=filter(rE5swide, Overlap=="NonOverlap")$HighLoad_Congruent),
               color="gray80") +
  labs(title = "Non-Overlap", x = "VSTM Load", y = "Reaction Time (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(500, 1200), clip = "on") +
  scale_y_continuous(breaks=c(500,600,700,800,900,1000,1100,1200)) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        legend.background = element_blank(),
        legend.position = c(.35, .85),
        axis.title.x = element_blank())

r2 <- ggplot() + 
  geom_bar(data=filter(rE5g, Overlap=="Overlap"), aes(x=vstmLoad, y=RT, fill=Congruency),
           stat="identity", width=0.7, color="black", position=position_dodge(.8)) + 
  geom_linerange(data=filter(rE5g, Overlap=="Overlap"), 
                 aes(x=vstmLoad, ymin=RT-ci, ymax=RT+ci, group=Congruency),
                 size=1, position=position_dodge(0.8)) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  geom_point(data=filter(rE5slong, Overlap=="Overlap"), 
             aes(x=vstmLoad, y=RT, group=Congruency),
             position=position_dodge(0.6), color="gray80", size=1.8) +
  geom_segment(data=filter(rE5swide, Overlap=="Overlap"), 
               aes(x=1-.15, y=filter(rE5swide, Overlap=="Overlap")$LowLoad_Incongruent,
                   xend=1+.15, yend=filter(rE5swide, Overlap=="Overlap")$LowLoad_Congruent),
               color="gray80") +
  geom_segment(data=filter(rE5swide, Overlap=="Overlap"), 
               aes(x=2-.15, y=filter(rE5swide, Overlap=="Overlap")$HighLoad_Incongruent,
                   xend=2+.15, yend=filter(rE5swide, Overlap=="Overlap")$HighLoad_Congruent),
               color="gray80") +
  labs(title = "Overlap", x = "VSTM Load", y = "Reaction Time (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(500, 1200), clip = "on") +
  scale_y_continuous(breaks=c(500,600,700,800,900,1000,1100,1200)) +
  theme_bw(base_size = 18) +
  theme(legend.position="none",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))

z1 <- ggplot(filter(rE5CEslong, Overlap=="NonOverlap"), aes(x=vstmLoad, y=cEffect)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  geom_point(color="gray80", size=1.8) +
  geom_segment(data=rE5CEswide, 
               aes(x=1, y=rE5CEswide$NonOverlap_LowLoad, xend=2, 
                   yend=rE5CEswide$NonOverlap_HighLoad), color="gray80") +
  geom_pointrange(filter(rE5CEg, Overlap=="NonOverlap"), inherit.aes=FALSE,
                  mapping=aes(x = vstmLoad, y=cEffect, 
                              ymin = cEffect - ci, ymax = cEffect + ci), 
                  colour="darkred", size = 1) +
  labs(x = "VSTM Load", y = "Congruency Effect (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(-50, 200), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

z2 <- ggplot(filter(rE5CEslong, Overlap=="Overlap"), aes(x=vstmLoad, y=cEffect)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  geom_point(color="gray80", size=1.8) +
  geom_segment(data=rE5CEswide, 
               aes(x=1, y=rE5CEswide$Overlap_LowLoad, xend=2, 
                   yend=rE5CEswide$Overlap_HighLoad), color="gray80") +
  geom_pointrange(filter(rE5CEg, Overlap=="Overlap"), inherit.aes=FALSE,
                  mapping=aes(x = vstmLoad, y=cEffect, 
                              ymin = cEffect - ci, ymax = cEffect + ci), 
                  colour="darkred", size = 1) +
  labs(x = "VSTM Load", y = "Congruency Effect (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(-50, 200), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y = element_blank())

(r1 | r2) / (z1 | z2)
```



### ANOVA
#### Mean RTs
```{r 8con_rt_anova, warning=FALSE, message=FALSE}
rt8con.aov <-  aov_ez(id = "SN", data = rE5, dv = "RT", within = c("Overlap", "vstmLoad", "Congruency")) 
rt8con.aov %>% anova(es = "pes") %>% kable(digits = 4)
```

#### Congruency Effects
```{r congruency_anova, warning=FALSE, message=FALSE}
rt4con.aov <-  aov_ez(id = "SN", data = rE5CEslong, dv = "cEffect", within = c("Overlap", "vstmLoad")) 
rt4con.aov %>% anova(es = "pes") %>% kable(digits = 4)
```


<br><br>

****

<br><br>


# Session Info
```{r sinfo, collapse=TRUE}
sessionInfo()
```


