---
title: "Experiment 3 (Blocked 0 vs. 4)"
author: "Hyuksu Lee, Do-Joon Yi"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapse: false
      smooth_scroll: false
    number_sections: true
    theme: cosmo 
    highlight: haddock
    code_folding: hide
subtitle: Effects of visual short-term memory load on response selection
mainfont: Noto Sans CJK KR
---

```{r wd, echo=FALSE}
setwd("~/Documents/GitHub/vstmAS/")
```

```{css, echo=FALSE}
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
```

```{r setup, message=FALSE}
set.seed(12345) # for reproducibility

# Some packages need to be loaded. We use `pacman` as a package manager, which takes care of the other packages. 
if (!require("pacman", quietly = TRUE)) install.packages("pacman")
if (!require("Rmisc", quietly = TRUE)) install.packages("Rmisc") # Never load it directly.
pacman::p_load(tidyverse, knitr,
               powerAnalysis, afex, emmeans, BayesFactor, 
               ggstatsplot)
pacman::p_load_gh("thomasp85/patchwork", "RLesur/klippy")

options(knitr.kable.NA = '')
options(dplyr.summarise.inform=FALSE) # 200603 supress warning in regards to regrouping 
klippy::klippy()
```

# Data

A short version of task description here.

```{r data, collapse=TRUE}
E3 <- read.csv("data/data_vstmAS3.csv", header = T)

E3$SN <- factor(E3$SN)
E3$vstmLoad <- factor(E3$vstmLoad, levels=c(1,2), labels=c("LowLoad","HighLoad"))
E3$Congruency <- factor(E3$Congruency, levels=c(0,1), labels=c("Incongruent","Congruent"))
E3$Corr <- ifelse(E3$Targ==E3$Resp,1,0)
E3$vstmCorr <- ifelse(E3$vstmLoad=="LowLoad",1,ifelse(E3$vstmCond==E3$vstmResp,1,0))

# Description of raw data columns.
# 1. SN: participant ID
# 2. Trial: 1~192
# 3. Block: 1~4
# 4. vstmLoad: VSTM load. 1 = low, 2 = high
# 5. Targ: target type. 1 or 2
# 6. Flnk: flanker type. 1 or 2
# 7. TargPos: target position. 1~6
# 8. FlnkPos: flanker position. 1 or 2
# 9. Congruency: 0 = incongruent, 1 = congruent
# 10. Resp: 1 or 2, 7 = no response
# 11. RT: response time in second
# 12. vstmCond: change = 1 or not = 2
# 13. vstmResp: 1 or 2, 7 = no response
# 14. vstmRT: response time in second
# 15. Corr: attention task correctness, 1=correct, 0 = incorrect
# 16. vstmCorr: VSTM task correctness, 1=correct, 0 = incorrect

glimpse(E3, width=70)

```

Both **VSTM Load** and **Congruency** were within-subject factors.

```{r design}
table(E3$vstmLoad, E3$SN) %>% kable()
table(E3$Congruency, E3$SN) %>% kable()
```


<br><br>

****

<br><br>


# Change Detection Task

## Accuracy

```{r vstm_sum, fig.asp=.5}
vE3s <- E3 %>% filter(vstmLoad == "HighLoad") %>% 
  group_by(SN) %>% 
  summarise(vstmCorr = mean(vstmCorr)*100) %>% 
  ungroup()

ggplot(data=vE3s, aes(x=1, y=vstmCorr)) +
  geom_violin(width = 1, trim = TRUE) +
  ggbeeswarm::geom_quasirandom(dodge.width = 0.7, color = "blue", size = 3, alpha = 0.2,
                               show.legend = FALSE) +
  stat_summary(fun.data = "mean_cl_boot", color = "darkred", size = 1) +
  coord_flip(ylim = c(50, 100), clip = "on") +
  labs(y = "Change Detection Accuracy") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        aspect.ratio = .3)
```

The mean accuracy of the change detection task was `r round(mean(vE3s$vstmCorr), digits=2)`%, which was comparable to 79.43% in the `high load` condition of Experiment 1.

<br><br>

****

<br><br>



# Flanker Task

Accuracy in the attention task was generally high. There were no significant effects in the ANOVA. 

## Accuracy

```{r acc_sum}
# Attention, Experiment 3, subject-level, long format
aE3slong <- E3 %>% group_by(SN, vstmLoad, Congruency) %>% 
  summarise(Accuracy = mean(Corr)*100) %>% 
  ungroup()

# Experiment 2 summary
aE3slong %>% group_by(vstmLoad, Congruency) %>% 
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup() %>% 
  kable()

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
aE3g <- Rmisc::summarySEwithin(data = aE3slong, measurevar = "Accuracy", 
                       withinvars = c("vstmLoad", "Congruency"), idvar = "SN") 

ggplot(data=aE3slong, aes(x=vstmLoad, y=Accuracy, fill=Congruency)) +
  geom_violin(width = 0.7, trim=TRUE) +
  ggbeeswarm::geom_quasirandom(dodge.width = 0.7, color = "gray80", size = 3, alpha = 0.4, 
                               show.legend = FALSE) +
  geom_pointrange(data=aE3g,
                  aes(x = vstmLoad, ymin = Accuracy-ci, ymax = Accuracy+ci, color = Congruency),
                  position = position_dodge(0.7), color = "darkred", size = 1, show.legend = FALSE) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  labs(x = "VSTM Load", 
       y = "Accuracy (%)", 
       fill="Congruency") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) 
```

### ANOVA

```{r acc_aov, warning=FALSE, message=FALSE}
aov_ez(id = "SN", data = aE3slong, dv = "Accuracy", 
       within = c("vstmLoad", "Congruency")) %>% 
  anova(es = "pes") %>% kable(digits = 4)
```

<br><br>

****

<br><br>


## RT

### Trimming

```{r trimming}
# filtering out incorrect trials
cE3 <- E3 %>% filter(Corr==1 & vstmCorr==1) %>% mutate(RT = RT*1000)

# trimming by 2.5 MAD.
rE3 <- cE3 %>% filter(RT > 200) %>% 
  group_by(SN) %>% 
  nest() %>%
  mutate(lbound = map(data, ~median(.$RT)-2.5*mad(.$RT)),
         ubound = map(data, ~median(.$RT)+2.5*mad(.$RT))) %>%
  unnest(c(lbound, ubound)) %>%
  unnest(data) %>%
  mutate(Outlier = (RT < lbound)|(RT > ubound)) %>%
  filter(Outlier == FALSE) %>%
  ungroup %>%
  select(SN, vstmLoad, Congruency, RT)

# percentage trimmed.
(nrow(cE3)-nrow(rE3))/nrow(cE3)
```

`r round(100*(nrow(cE3)-nrow(rE3))/nrow(cE3), digits=2)`%의 가외치가 제거되었다.

```{r rt_distribution, fig.asp = .4}
den1 <- ggplot(cE3, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den2 <- ggplot(rE3, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) + 
  labs(x = "Trimmed RT") + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den1 + den2
```


### Mean RT

```{r rt_sum}
# Attention RT, Experiment 1, subject-level, long format
rE3slong <- rE3 %>% group_by(SN, vstmLoad, Congruency) %>% 
  summarise(RT = mean(RT)) %>% 
  ungroup()

# Experiment 1 summary
rE3slong %>% group_by(vstmLoad, Congruency) %>% 
  summarise(M = mean(RT), SD = sd(RT)) %>% 
  ungroup() %>% 
  kable()
```

### RT Congruency Effect

```{r congruency_sum}
# Experiment 1 Congruency Effect in RT, subject-level, long format
rE3CEslong <- rE3slong %>%
  spread(key = Congruency, value = RT) %>% 
  mutate(cEffect = Incongruent - Congruent) %>% 
  select(SN, vstmLoad, cEffect)

# Experiment 1 summary
rE3CEslong %>% group_by(vstmLoad) %>% 
  summarise(M = mean(cEffect), SD = sd(cEffect)) %>% 
  ungroup() %>% 
  kable()

# group level, needed for printing & geom_pointrange
rE3g <- Rmisc::summarySEwithin(data = rE3slong, measurevar = "RT", 
                               withinvars = c("vstmLoad", "Congruency"), idvar = "SN") 

rE3swide <- rE3slong %>%  # wide format, needed for geom_segments.
  unite("temp", c("vstmLoad", "Congruency")) %>% 
  spread(key = temp, value = RT)

G1 <- ggplot() + 
  geom_bar(data=rE3g, aes(x=vstmLoad, y=RT, fill=Congruency),
           stat="identity", width=0.7, color="black", position=position_dodge(.8)) + 
  geom_linerange(data=rE3g, aes(x=vstmLoad, ymin=RT-ci, ymax=RT+ci, group=Congruency),
                 size=1, position=position_dodge(0.8)) +
  scale_fill_manual(values=c('#0073C2FF','#EFC000FF'),
                    labels=c("Incongruent", "Congruent")) +
  geom_point(data=rE3slong, aes(x=vstmLoad, y=RT, group=Congruency),
             position=position_dodge(0.6), color="gray80", size=1.8) +
  geom_segment(data=rE3swide, aes(x=1-.15, y=LowLoad_Incongruent, 
                                    xend=1+.15, yend=LowLoad_Congruent),
               color="gray80") +
  geom_segment(data=rE3swide, aes(x=2-.15, y=HighLoad_Incongruent, 
                                    xend=2+.15, yend=HighLoad_Congruent),
               color="gray80") +
  labs(x = "VSTM Load", y = "Reaction Time (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  coord_cartesian(ylim = c(500, 1300), clip = "on") +
  scale_y_continuous(breaks=c(500,700,900,1100,1300)) +
  theme_bw(base_size = 18) +
  theme(legend.position="top",
        legend.spacing.x = unit(0.5, 'lines'),
        legend.title = element_blank(),
        legend.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

# group level, needed for printing & geom_pointrange
rE3CEg <- Rmisc::summarySEwithin(data = rE3CEslong, measurevar = "cEffect", 
                                withinvars = "vstmLoad", idvar = "SN") 

# wide format, needed for geom_segments.
rE3CEswide <- rE3CEslong %>%  spread(key = vstmLoad, value = cEffect)

G2 <- ggplot(rE3CEslong, aes(x=vstmLoad, y=cEffect)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  geom_point(color="gray80", size=1.8) +
  geom_segment(data=rE3CEswide, color="gray80", 
               aes(x=1, y=LowLoad, xend=2, yend=HighLoad)) +
  geom_pointrange(rE3CEg, inherit.aes=FALSE,
                  mapping=aes(x = vstmLoad, y=cEffect, 
                              ymin = cEffect - ci, ymax = cEffect + ci), 
                  colour="darkred", size = 1)+
  # labs(x = "VSTM Load", y = "Congruency Effect \n (Incongruent - Congruent)") +
  labs(x = "VSTM Load", y = "Congruency Effect (ms)") +
  scale_x_discrete(labels=c("LowLoad" = "Low", "HighLoad" = "High")) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

# Multipanel plot
G1 + G2 + plot_layout(nrow = 1, widths = c(2, 1.3))
```


### ANOVA & Post-hoc

```{r rt_aov, warning=FALSE, message=FALSE}
rt.aov <- aov_ez(id = "SN", dv = "RT", data = rE3, within = c("vstmLoad", "Congruency")) 
rt.aov %>% anova(es = "pes") %>% kable(digits = 4)

emmeans(rt.aov, pairwise ~ Congruency | vstmLoad)$contrasts %>% kable()
```


### Bayes Factor

ANOVA에서 BF를 쓰려면 여러가지 복잡한 사안들을 결정해야 한다. 본 연구의 가설은 congruency effect에 집중하는 만큼, `low load`와 `high load`의 차이만 비교하기로 한다. 

```{r}
rE3CEswide$CongEffDiff <- rE3CEswide$LowLoad - rE3CEswide$HighLoad
( bf <- ttestBF(x = rE3CEswide$CongEffDiff) )

1/bf
```

<br><br>

****

<br><br>


# Session Info
```{r sinfo, collapse=TRUE}
sessionInfo()
```


